\Title

### 2021-06-07 manuscript/content.tex
Extend comments on damping parameter

To solve this issue, we first scale the Jacobian matrix so that its elements
are unitless and each column has unit variance.
We define a diagonal matrix $\mathbf{S}$

@@

\noindent where $\mathbf{B}$ is the scaled and unitless Jacobian matrix and
$\mathbf{m}$ is a vector containing scaled coefficients with the same units as
the data.

@@

\noindent where $\lambda$ is a \emph{dimensionless} damping parameter and
regularization is applied on the scaled coefficients $\mathbf{m}$ instead of
$\mathbf{c}$.
From experience, we recommend searching for suitable $\lambda$ values between
$10^{-8}$ and $10^{2}$ varying by order-of-magnitude, irrespective of the
dataset.

>>>>

To solve this issue, we first scale the Jacobian matrix so that its elements
are dimensionless and each column has unit variance.
We define a diagonal matrix $\mathbf{S}$

@@

\noindent where $\mathbf{B}$ is the scaled and dimensionless Jacobian matrix
and $\mathbf{m}$ is a vector containing scaled coefficients with the same units
as the data.

@@

\noindent where $\lambda$ is a \emph{dimensionless} damping parameter and
regularization is applied on the scaled coefficients $\mathbf{m}$ instead of
$\mathbf{c}$.
Using a dimensionless damping parameter allows us to narrow the range of values
of $\lambda$ that would generate the most accurate predictions, irrespective
of the dataset and its units.
The damping parameter controls the amount of regularization that is be applied:
a large damping value would generate smooth solutions that fail to reproduce
the high frequency components, while a small value would overfit the data,
failing to produce accurate predictions.
From experience, we recommend searching for suitable $\lambda$ values between
$10^{-6}$ and $10^{4}$ varying by order-of-magnitude, irrespective of the
dataset.
The choice of the damping and any other hyper-parameter could be done through
validation methods, such as cross-validation algorithms.
